---
title: "index.Rmd"
author: "Eline DENIS"
date: "2025-08-18"
output: html_document
site: bookdown::bookdown_site
output:
  bookdown::gitbook:
    toc: true
    number_sections: true
    split_by: section
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = "/media/labct/P4/Single_cell_rna_seq_analyses_eline/sc3samples_whitelist")
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Introduction
start by running the blaze preprocessing file in the rootdir
blabla
pour render le bookdown:
bookdown::render_book("index.Rmd", "bookdown::gitbook")

structure du dossier vignette:


mon_projet_bookdown/
├── index.Rmd
├── 01-analyse.Rmd
├── 02-resultats.Rmd
├── fonctions/
│   └── fonctions.R     <- tes fonctions, pas affiché
├── data/
│   └── jeu.RDS         <- tes données
├── _bookdown.yml
├── _output.yml

/scratch/nautilus/users/edenis2023@ec-nantes.fr

setting a working directory for the rest of the analysis:
```{r}
rootdir="/media/labct/P4/Single_cell_rna_seq_analyses_eline/vignette_data"
```
